---
title: "Enhanced TBI Analysis: Hierarchical Testing + Elastic Net Regularization"
output: html_notebook
---

```{r setup, include=FALSE}
# Load necessary libraries
knitr::opts_knit$set(root.dir = 'C:/Users/jonat/Documents/SNIRP-Thesis/ROI-Flat File Generation/For Export')
library(tidyverse)
library(lme4)
library(lmerTest)
library(glmnet)
library(caret)
library(lubridate)
library(tidymodels)
library(janitor)
library(broom.mixed)
library(doParallel)
library(foreach)
library(performance)
library(pROC)
tidymodels_prefer()
set.seed(333)
```

## Enhanced Analysis Overview

This enhanced analysis implements two key improvements:
1. **Hierarchical Multiple Testing Correction** - FDR correction within brain systems
2. **Elastic Net Regularization** - Feature selection and regularization for high-dimensional data

## Data Import and Preparation

```{r data-import}
# Load datasets (same as before)
Severity <- read_csv('Data Import/Final_TBI_With_Severity.csv')
GM <- read_csv('1_to_1Matching/merged_GM_2024-02-23.csv')
WM <- read_csv('1_to_1Matching/merged_WM_2024-02-23.csv')
Thick <- read_csv('1_to_1Matching/merged_Thick_2024-02-23.csv')
CSF <- read_csv('1_to_1Matching/merged_CSF_2024-02-23.csv')

# Merge severity data and clean column names
datasets <- list(GM = GM, WM = WM, Thick = Thick, CSF = CSF)
datasets <- lapply(datasets, function(df) {
  df %>%
    left_join(Severity %>% select(RID, injury_severity), by = "RID") %>%
    mutate(injury_severity = ifelse(is.na(injury_severity), 0, injury_severity)) %>%
    clean_names()
})

GM <- datasets$GM
WM <- datasets$WM
Thick <- datasets$Thick
CSF <- datasets$CSF
```

## Define Brain System Hierarchies

```{r brain-systems}
# Define anatomically-informed ROI groupings for hierarchical testing
brain_systems <- list(
  
  # Frontal System
  frontal = c("right_mfg_middle_frontal_gyrus", "left_mfg_middle_frontal_gyrus",
              "right_sfg_superior_frontal_gyrus", "left_sfg_superior_frontal_gyrus",
              "right_msfg_superior_frontal_gyrus_medial_segment", "left_msfg_superior_frontal_gyrus_medial_segment",
              "right_mfc_medial_frontal_cortex", "left_mfc_medial_frontal_cortex",
              "right_fo_frontal_operculum", "left_fo_frontal_operculum",
              "right_frp_frontal_pole", "left_frp_frontal_pole",
              "right_op_ifg_opercular_part_of_the_inferior_frontal_gyrus", 
              "left_op_ifg_opercular_part_of_the_inferior_frontal_gyrus",
              "right_or_ifg_orbital_part_of_the_inferior_frontal_gyrus",
              "left_or_ifg_orbital_part_of_the_inferior_frontal_gyrus",
              "right_tr_ifg_triangular_part_of_the_inferior_frontal_gyrus",
              "left_tr_ifg_triangular_part_of_the_inferior_frontal_gyrus"),
  
  # Temporal System
  temporal = c("right_mtg_middle_temporal_gyrus", "left_mtg_middle_temporal_gyrus",
               "right_stg_superior_temporal_gyrus", "left_stg_superior_temporal_gyrus",
               "right_itg_inferior_temporal_gyrus", "left_itg_inferior_temporal_gyrus",
               "right_tmp_temporal_pole", "left_tmp_temporal_pole",
               "right_ttg_transverse_temporal_gyrus", "left_ttg_transverse_temporal_gyrus",
               "right_pt_planum_temporale", "left_pt_planum_temporale",
               "right_pp_planum_polare", "left_pp_planum_polare"),
  
  # Parietal System  
  parietal = c("right_spl_superior_parietal_lobule", "left_spl_superior_parietal_lobule",
               "right_po_g_postcentral_gyrus", "left_po_g_postcentral_gyrus",
               "right_m_po_g_postcentral_gyrus_medial_segment", 
               "left_m_po_g_postcentral_gyrus_medial_segment",
               "right_smg_supramarginal_gyrus", "left_smg_supramarginal_gyrus",
               "right_an_g_angular_gyrus", "left_an_g_angular_gyrus",
               "right_po_parietal_operculum", "left_po_parietal_operculum"),
  
  # Occipital System
  occipital = c("right_sog_superior_occipital_gyrus", "left_sog_superior_occipital_gyrus",
                "right_mog_middle_occipital_gyrus", "left_mog_middle_occipital_gyrus",
                "right_iog_inferior_occipital_gyrus", "left_iog_inferior_occipital_gyrus",
                "right_ocp_occipital_pole", "left_ocp_occipital_pole",
                "right_calc_calcarine_cortex", "left_calc_calcarine_cortex",
                "right_cun_cuneus", "left_cun_cuneus"),
  
  # Limbic System
  limbic = c("right_hippocampus", "left_hippocampus",
             "right_amygdala", "left_amygdala",
             "right_phg_parahippocampal_gyrus", "left_phg_parahippocampal_gyrus",
             "right_ent_entorhinal_area", "left_ent_entorhinal_area",
             "right_a_cg_g_anterior_cingulate_gyrus", "left_a_cg_g_anterior_cingulate_gyrus",
             "right_p_cg_g_posterior_cingulate_gyrus", "left_p_cg_g_posterior_cingulate_gyrus",
             "right_m_cg_g_middle_cingulate_gyrus", "left_m_cg_g_middle_cingulate_gyrus"),
  
  # Subcortical System
  subcortical = c("right_caudate", "left_caudate",
                  "right_putamen", "left_putamen", 
                  "right_pallidum", "left_pallidum",
                  "right_thalamus_proper", "left_thalamus_proper",
                  "right_accumbens_area", "left_accumbens_area",
                  "right_ventral_dc", "left_ventral_dc"),
  
  # Ventricular System
  ventricular = c("x3rd_ventricle", "x4th_ventricle",
                  "right_lateral_ventricle", "left_lateral_ventricle",
                  "right_inf_lat_vent", "left_inf_lat_vent", "csf")
)

print("Brain system groupings defined:")
sapply(brain_systems, length)
```

## Data Transformation (Same as Before)

```{r data-transformation}
# Apply transformations (keeping existing transformation code)
apply_transformations <- function(df) {
  df %>%
    mutate(
      months_since_bl_exam = as.numeric(difftime(ymd(examdate), ymd(examdate_bl), units = "days")) / 30.44,
      new_injury_severity = factor(case_when(
        injury_severity %in% c(0, 1) ~ as.character(injury_severity),
        injury_severity %in% c(2, 3, 4) ~ "2",
        TRUE ~ NA_character_
      )),
      ptgender = factor(ptgender, levels = c('Female', 'Male')),
      pteducat = as.numeric(pteducat),
      apoe4 = factor(apoe4, levels = c('0', '1', '2')),
      tbi = as.factor(tbi),
      examdate = ymd(examdate),
      new_injury_severity = factor(new_injury_severity, levels = c("0", "1", "2")),
      dx = ifelse(is.na(dx), as.character(dx_bl), as.character(dx)),
      dx = case_when(
        dx %in% c('LMCI', 'EMCI', 'SMC') ~ 'MCI',
        TRUE ~ as.character(dx)
      ),
      dx = factor(dx, levels = c("CN", "MCI", "Dementia"))
    )
}

# Apply transformations
Thick_transformed <- apply_transformations(Thick)
GM_transformed <- apply_transformations(GM)
CSF_transformed <- apply_transformations(CSF)
WM_transformed <- apply_transformations(WM)

# Get ROI lists (remove medial wall for thickness)
Thick_transformed <- Thick_transformed %>% select(-l_medial_wall, -r_medial_wall)
Thick_ROIs <- names(Thick_transformed)[8:157]
```

## Enhanced Analysis Functions

### 1. Hierarchical Multiple Testing Correction

```{r hierarchical-testing-functions}
# Function to apply hierarchical FDR correction
apply_hierarchical_fdr <- function(results_df, brain_systems, roi_column = "Outcome_Variable") {
  
  # Initialize new columns
  results_df$p.value.system_adjusted <- results_df$p.value
  results_df$brain_system <- "Other"
  
  # Assign brain systems
  for(system_name in names(brain_systems)) {
    system_mask <- results_df[[roi_column]] %in% brain_systems[[system_name]]
    results_df$brain_system[system_mask] <- system_name
  }
  
  # Apply FDR correction within each brain system
  for(system_name in names(brain_systems)) {
    system_mask <- results_df$brain_system == system_name
    if(sum(system_mask) > 0) {
      system_pvals <- results_df$p.value[system_mask]
      results_df$p.value.system_adjusted[system_mask] <- p.adjust(system_pvals, method = "BH")
    }
  }
  
  # Also keep global FDR for comparison
  results_df$p.value.global_adjusted <- p.adjust(results_df$p.value, method = "BH")
  
  return(results_df)
}

# Function to summarize hierarchical testing results
summarize_hierarchical_results <- function(results_df, alpha = 0.05) {
  
  summary_stats <- results_df %>%
    group_by(brain_system) %>%
    summarise(
      n_rois = n(),
      n_significant_uncorrected = sum(p.value < alpha, na.rm = TRUE),
      n_significant_system_fdr = sum(p.value.system_adjusted < alpha, na.rm = TRUE),
      n_significant_global_fdr = sum(p.value.global_adjusted < alpha, na.rm = TRUE),
      proportion_system_fdr = n_significant_system_fdr / n_rois,
      proportion_global_fdr = n_significant_global_fdr / n_rois,
      .groups = 'drop'
    ) %>%
    arrange(desc(proportion_system_fdr))
  
  return(summary_stats)
}
```

### 2. Elastic Net Regularization Functions

```{r elastic-net-functions}
# Function to prepare data for elastic net
prepare_elastic_net_data <- function(data, outcome_vars, exclude_vars = NULL) {
  
  # Define predictor variables (all ROIs + covariates)
  predictor_vars <- c(outcome_vars, "months_since_bl_exam", "age", "ptgender", "apoe4", "dx")
  if(!is.null(exclude_vars)) {
    predictor_vars <- setdiff(predictor_vars, exclude_vars)
  }
  
  # Create model matrix
  formula_str <- paste("~", paste(predictor_vars, collapse = " + "))
  model_matrix <- model.matrix(as.formula(formula_str), data = data)[, -1]  # Remove intercept
  
  return(list(
    X = model_matrix,
    predictor_names = colnames(model_matrix),
    complete_cases = complete.cases(model_matrix)
  ))
}

# Function to run elastic net analysis for TBI prediction
elastic_net_tbi_prediction <- function(data, outcome_vars, alpha_values = seq(0, 1, 0.1)) {
  
  # Prepare data
  elastic_data <- prepare_elastic_net_data(data, outcome_vars)
  
  # Filter to complete cases
  complete_idx <- elastic_data$complete_cases
  X <- elastic_data$X[complete_idx, ]
  y <- data$new_injury_severity[complete_idx]
  
  # Convert to binary (TBI vs no TBI) for logistic regression
  y_binary <- ifelse(y == "0", 0, 1)
  
  # Cross-validation to find optimal parameters
  cv_results <- list()
  best_model <- NULL
  best_auc <- 0
  
  for(alpha in alpha_values) {
    cv_fit <- cv.glmnet(X, y_binary, family = "binomial", alpha = alpha, 
                        nfolds = 10, type.measure = "auc")
    
    # Get AUC at lambda.1se (more parsimonious model)
    auc_1se <- max(cv_fit$cvm[cv_fit$lambda == cv_fit$lambda.1se])
    
    cv_results[[paste0("alpha_", alpha)]] <- list(
      cv_fit = cv_fit,
      auc = auc_1se,
      alpha = alpha,
      lambda_1se = cv_fit$lambda.1se,
      lambda_min = cv_fit$lambda.min
    )
    
    if(auc_1se > best_auc) {
      best_auc <- auc_1se
      best_model <- cv_results[[paste0("alpha_", alpha)]]
    }
  }
  
  # Fit final model with best parameters
  final_model <- glmnet(X, y_binary, family = "binomial", 
                       alpha = best_model$alpha, lambda = best_model$lambda_1se)
  
  # Extract coefficients
  coefficients <- coef(final_model, s = best_model$lambda_1se)
  coef_df <- data.frame(
    variable = rownames(coefficients),
    coefficient = as.vector(coefficients),
    stringsAsFactors = FALSE
  ) %>%
    filter(coefficient != 0, variable != "(Intercept)") %>%
    arrange(desc(abs(coefficient)))
  
  return(list(
    best_model = best_model,
    final_model = final_model,
    coefficients = coef_df,
    cv_results = cv_results,
    X = X,
    y = y_binary,
    best_auc = best_auc
  ))
}

# Function for elastic net feature selection in longitudinal models
elastic_net_feature_selection <- function(data, outcome_var, predictor_vars, 
                                        alpha_values = seq(0, 1, 0.1)) {
  
  # Prepare data for feature selection
  complete_data <- data[complete.cases(data[, c(outcome_var, predictor_vars)]), ]
  
  X <- as.matrix(complete_data[, predictor_vars])
  y <- complete_data[[outcome_var]]
  
  # Cross-validation for parameter selection
  best_model <- NULL
  best_mse <- Inf
  
  for(alpha in alpha_values) {
    cv_fit <- cv.glmnet(X, y, alpha = alpha, nfolds = 10)
    mse_1se <- min(cv_fit$cvm)
    
    if(mse_1se < best_mse) {
      best_mse <- mse_1se
      best_model <- list(
        cv_fit = cv_fit,
        alpha = alpha,
        lambda_1se = cv_fit$lambda.1se,
        mse = mse_1se
      )
    }
  }
  
  # Extract selected features
  final_model <- glmnet(X, y, alpha = best_model$alpha, lambda = best_model$lambda_1se)
  coefficients <- coef(final_model, s = best_model$lambda_1se)
  
  selected_features <- rownames(coefficients)[coefficients[, 1] != 0]
  selected_features <- selected_features[selected_features != "(Intercept)"]
  
  return(list(
    selected_features = selected_features,
    best_model = best_model,
    final_model = final_model,
    n_selected = length(selected_features),
    total_features = ncol(X)
  ))
}
```

## Enhanced Complete Analysis Function

```{r enhanced-complete-analysis}
# Enhanced analysis function combining LME + hierarchical testing + elastic net
perform_enhanced_analysis <- function(data, outcome_vars, filename_base, brain_systems) {
  
  cat("Starting enhanced analysis for", length(outcome_vars), "variables...\n")
  
  # Step 1: Traditional LME analysis (same as before)
  cat("Step 1: Running traditional LME models...\n")
  lme_results <- lapply(outcome_vars, function(var) {
    cat(sprintf("Modeling %s: %d of %d\n", var, which(outcome_vars == var), length(outcome_vars)))
    
    formula <- as.formula(paste(var, "~ new_injury_severity * months_since_bl_exam + 
                                age + ptgender + field + dx + tiv + apoe4 + (1|rid)"))
    
    model <- lmerTest::lmer(formula, data = data, REML = FALSE)
    
    # Cross-validation (keeping existing CV code)
    set.seed(333)
    cv_folds <- vfold_cv(data, v = 10, strata = !!sym(var))
    cv_results <- map(cv_folds$splits, ~{
      analysis_data <- analysis(.x)
      assessment_data <- assessment(.x)
      predictions <- predict(model, newdata = assessment_data, re.form = NA)
      observed <- assessment_data[[var]]
      data.frame(
        R_squared = cor(predictions, observed, use = "complete.obs")^2,
        RMSE = sqrt(mean((predictions - observed)^2))
      )
    })
    
    cv_summary <- summarise(bind_rows(cv_results), 
                           Avg_R_squared = mean(R_squared, na.rm = TRUE), 
                           Avg_RMSE = mean(RMSE, na.rm = TRUE))
    
    fixed_effects <- broom.mixed::tidy(model)
    conf_int <- confint(model, level = 0.95) %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column("term") %>% 
      dplyr::rename(lower = 2, upper = 3)
    
    inferential_stats_df <- fixed_effects %>%
      left_join(conf_int, by = "term") %>%
      mutate(Outcome_Variable = var, 
             Avg_R_squared = cv_summary$Avg_R_squared, 
             Avg_RMSE = cv_summary$Avg_RMSE, 
             BIC = BIC(model))
    
    return(inferential_stats_df)
  })
  
  # Combine LME results
  all_lme_results <- bind_rows(lme_results, .id = "ID")
  
  # Step 2: Apply hierarchical multiple testing correction
  cat("Step 2: Applying hierarchical multiple testing correction...\n")
  hierarchical_results <- apply_hierarchical_fdr(all_lme_results, brain_systems)
  
  # Step 3: Elastic net feature selection
  cat("Step 3: Running elastic net feature selection...\n")
  
  # 3a: TBI prediction using all ROIs
  tbi_prediction <- elastic_net_tbi_prediction(data, outcome_vars)
  
  # 3b: Feature selection for each significant system
  system_feature_selection <- list()
  
  # Get systems with significant effects
  system_summary <- summarize_hierarchical_results(hierarchical_results)
  significant_systems <- system_summary$brain_system[system_summary$n_significant_system_fdr > 0]
  
  for(system in significant_systems) {
    system_rois <- brain_systems[[system]]
    available_rois <- intersect(system_rois, outcome_vars)
    
    if(length(available_rois) > 5) {  # Only run if sufficient ROIs
      cat(sprintf("Feature selection for %s system (%d ROIs)...\n", system, length(available_rois)))
      
      system_feature_selection[[system]] <- elastic_net_feature_selection(
        data, "new_injury_severity", available_rois
      )
    }
  }
  
  # Step 4: Generate comprehensive results
  cat("Step 4: Generating comprehensive results...\n")
  
  # Save hierarchical testing results
  write_csv(hierarchical_results, paste0(filename_base, "_hierarchical.csv"))
  
  # Save system summary
  write_csv(system_summary, paste0(filename_base, "_system_summary.csv"))
  
  # Save elastic net results
  if(!is.null(tbi_prediction$coefficients)) {
    write_csv(tbi_prediction$coefficients, paste0(filename_base, "_elastic_net_tbi_prediction.csv"))
  }
  
  # Save feature selection results
  if(length(system_feature_selection) > 0) {
    feature_summary <- map_dfr(system_feature_selection, function(x) {
      data.frame(
        n_selected = x$n_selected,
        total_features = x$total_features,
        proportion_selected = x$n_selected / x$total_features
      )
    }, .id = "brain_system")
    
    write_csv(feature_summary, paste0(filename_base, "_feature_selection_summary.csv"))
  }
  
  return(list(
    hierarchical_results = hierarchical_results,
    system_summary = system_summary,
    tbi_prediction = tbi_prediction,
    feature_selection = system_feature_selection,
    original_results = all_lme_results
  ))
}
```

## Run Enhanced Analysis

```{r run-enhanced-analysis}
# Define outcome variables for each dataset
outcome_vars_thickness <- Thick_ROIs
outcome_vars_csf <- names(CSF_transformed)[8:ncol(CSF_transformed)]
outcome_vars_gm <- names(GM_transformed)[8:ncol(GM_transformed)]  
outcome_vars_wm <- names(WM_transformed)[8:ncol(WM_transformed)]

# Remove non-ROI columns from outcome variables
exclude_pattern <- "rid|examdate|scan_date|field|scan|dx_bl|dx|viscode|ptid|tbi|months_since_bl_exam|age|ptgender|pteducat|apoe4|injury_severity|new_injury_severity|tiv|cdrsb"

outcome_vars_csf <- outcome_vars_csf[!grepl(exclude_pattern, outcome_vars_csf, ignore.case = TRUE)]
outcome_vars_gm <- outcome_vars_gm[!grepl(exclude_pattern, outcome_vars_gm, ignore.case = TRUE)]
outcome_vars_wm <- outcome_vars_wm[!grepl(exclude_pattern, outcome_vars_wm, ignore.case = TRUE)]

# Run enhanced analysis for each modality
cat("=== ENHANCED ANALYSIS: CORTICAL THICKNESS ===\n")
thickness_enhanced <- perform_enhanced_analysis(
  Thick_transformed, outcome_vars_thickness, "Enhanced_Thickness", brain_systems
)

cat("=== ENHANCED ANALYSIS: CSF VOLUME ===\n")
csf_enhanced <- perform_enhanced_analysis(
  CSF_transformed, outcome_vars_csf, "Enhanced_CSF", brain_systems
)

cat("=== ENHANCED ANALYSIS: GRAY MATTER VOLUME ===\n")
gm_enhanced <- perform_enhanced_analysis(
  GM_transformed, outcome_vars_gm, "Enhanced_GM", brain_systems
)

cat("=== ENHANCED ANALYSIS: WHITE MATTER VOLUME ===\n")
wm_enhanced <- perform_enhanced_analysis(
  WM_transformed, outcome_vars_wm, "Enhanced_WM", brain_systems
)
```

## Results Summary

```{r results-summary}
# Create comprehensive results summary
cat("=== ENHANCED ANALYSIS SUMMARY ===\n\n")

modalities <- list(
  "Cortical Thickness" = thickness_enhanced,
  "CSF Volume" = csf_enhanced,
  "Gray Matter Volume" = gm_enhanced,
  "White Matter Volume" = wm_enhanced
)

for(modality_name in names(modalities)) {
  cat("### ", modality_name, "\n")
  
  results <- modalities[[modality_name]]
  
  # System-wise summary
  cat("**Brain Systems with Significant Effects:**\n")
  sig_systems <- results$system_summary %>%
    filter(n_significant_system_fdr > 0) %>%
    arrange(desc(proportion_system_fdr))
  
  if(nrow(sig_systems) > 0) {
    print(sig_systems)
  } else {
    cat("No significant effects after hierarchical correction.\n")
  }
  
  # Elastic net summary
  if(!is.null(results$tbi_prediction$best_auc)) {
    cat("\n**TBI Prediction Performance (Elastic Net):**\n")
    cat("Best AUC:", round(results$tbi_prediction$best_auc, 3), "\n")
    cat("Best alpha:", results$tbi_prediction$best_model$alpha, "\n")
    cat("Number of selected features:", nrow(results$tbi_prediction$coefficients), "\n")
    
    if(nrow(results$tbi_prediction$coefficients) > 0) {
      cat("\n**Top 10 Predictive Features:**\n")
      print(head(results$tbi_prediction$coefficients, 10))
    }
  }
  
  cat("\n", rep("=", 50), "\n\n")
}

# Overall comparison: Traditional vs Hierarchical correction
cat("=== CORRECTION METHOD COMPARISON ===\n")

comparison_summary <- map_dfr(modalities, function(x) {
  x$system_summary %>%
    summarise(
      total_rois = sum(n_rois),
      global_fdr_significant = sum(n_significant_global_fdr),
      hierarchical_fdr_significant = sum(n_significant_system_fdr),
      power_gain = hierarchical_fdr_significant - global_fdr_significant,
      .groups = 'drop'
    )
}, .id = "modality")

print(comparison_summary)
```

## Visualization of Enhanced Results

```{r enhanced-visualizations}
# Create enhanced visualization function
create_enhanced_brain_plot <- function(results, modality_name, save_plots = TRUE) {
  
  # Filter to significant results (hierarchical FDR)
  sig_results <- results$hierarchical_results %>%
    filter(p.value.system_adjusted < 0.05, 
           term %in% c("new_injury_severity1", "new_injury_severity2", 
                      "new_injury_severity1:months_since_bl_exam", 
                      "new_injury_severity2:months_since_bl_exam"))
  
  if(nrow(sig_results) == 0) {
    cat("No significant results for", modality_name, "\n")
    return(NULL)
  }
  
  # Create system-wise significance plot
  system_plot_data <- sig_results %>%
    group_by(brain_system, term) %>%
    summarise(
      n_significant = n(),
      mean_effect = mean(estimate, na.rm = TRUE),
      .groups = 'drop'
    )
  
  p1 <- ggplot(system_plot_data, aes(x = brain_system, y = n_significant, fill = term)) +
    geom_col(position = "dodge") +
    labs(title = paste("Significant Effects by Brain System:", modality_name),
         x = "Brain System", y = "Number of Significant ROIs",
         fill = "Term") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  # Effect size plot
  p2 <- ggplot(sig_results, aes(x = brain_system, y = estimate, color = term)) +
    geom_boxplot() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    labs(title = paste("Effect Sizes by Brain System:", modality_name),
         x = "Brain System", y = "Effect Size",
         color = "Term") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  if(save_plots) {
    ggsave(paste0("Enhanced_", gsub(" ", "_", modality_name), "_system_counts.png"), 
           p1, width = 12, height = 6)
    ggsave(paste0("Enhanced_", gsub(" ", "_", modality_name), "_effect_sizes.png"), 
           p2, width = 12, height = 6)
  }
  
  return(list(system_counts = p1, effect_sizes = p2))
}

# Create plots for each modality
modality_plots <- map(names(modalities), function(mod_name) {
  create_enhanced_brain_plot(modalities[[mod_name]], mod_name)
})
names(modality_plots) <- names(modalities)

# Display the plots
for(mod_name in names(modality_plots)) {
  if(!is.null(modality_plots[[mod_name]])) {
    print(modality_plots[[mod_name]]$system_counts)
    print(modality_plots[[mod_name]]$effect_sizes)
  }
}
```

## Conclusions

This enhanced analysis provides several key improvements:

1. **Hierarchical Multiple Testing**: Reduces Type I error while maintaining power within brain systems
2. **Elastic Net Regularization**: Identifies the most predictive features for TBI classification
3. **Feature Selection**: Reduces dimensionality while preserving biological interpretability
4. **Enhanced Visualization**: Shows results organized by brain systems

The combination of these methods provides a more powerful and interpretable analysis of TBI effects on brain structure.
